Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-08-22 analysis/paper/paper.Rmd
Address Reviewer 1 Comment #1

Reproducibility is one component under the umbrella of open science.
By proactively practicing open science, the work increases the chance to become more reproducible through the availability of data and code.
That is, open science leads to reproducibility and replicability.

>>>>

Reproducibility is one component under the umbrella of open science.
By proactively practising open science, the work increases the chance to become more reproducible through the availability of data and code.
That is, open science enables reproducibility and replicability.
